A simple probabilistic approach to finding strongly lensed quasars in ground-based imaging

### 2014-05-08 docs/paper1.tex
Getting up to date with Agnello...
Looking at plan

\title[Automated Gravitational Lens Detection]
{Automated Detection of Gravitationally Lensed Quasars in Multi-epoch
Ground-based Imaging Data}

\author[]{%
  Philip J. Marshall$^{1,2}$\thanks{\pjmemail},
  David W. Hogg$^{3}$,
  Dustin Lang$^{4}$,
  Eric P. Morganson$^{5}$ 
  \medskip\\
  $^1$\oxford\\
  $^2$\kipac\\
  $^3$\nyu\\
  $^4$\cmu\\
  $^5$\mpia
}

@@

\begin{abstract}
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION 2: SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Model}
\label{sec:model}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We thank X for useful discussions and suggestions.

>>>>

\title[Finding lensed quasars]
{A simple probabilistic approach to finding 
strongly lensed quasars in ground-based imaging}

\author[]{%
  Philip J. Marshall$^{1,2}$\thanks{\pjmemail},
  David W. Hogg$^{3,4}$,
  Adriano Agnello$^{5}$,
  Dustin Lang$^{6}$,
  Eric P. Morganson$^{4}$,
  and others 
  \medskip\\
  $^1$\kipac\\
  $^2$\oxford\\
  $^3$\nyu\\
  $^4$\mpia\\
  $^4$\ucsb\\
  $^6$\cmu
}

@@

\begin{abstract}
In some heuristic sense, we end up believing that a particular source
is a galaxy-scale strong gravitational lens because it is more
plausible to explain it as a superposition of a gravitationally
distorted background source and a foreground lensing galaxy than it is
to explain it as a single object with very odd morphology.  Here we
construct a quantitative approximation to this comparison of
plausibilities by fitting multi-epoch, multi-band ground-based imaging
of gravitational lens candidates with two image models, one of which, ``Lens,''
is a point source being lensed by a simple model massive galaxy, and the
other is a complex ``Nebula'' constructed from a simple galaxy and $K$
point sources.  The relative plausibility of the lensing hypothesis is
\emph{approximated} by a likelihood ratio between these models, evaluated at
best-fit (that is, not marginalized), penalized by a factor accounting
for relative model freedom.  We fit these models and compute lensing
plausibility for 
% four candidate lens sources with \panstarrs\ $grizY$ imaging.  
10 confirmed lensed quasars and 40 confirmed non-lenses from the SDSS Quasar Lens
Search (SQLS).
% Two of the sources are known lenses, and two are not;
We find that we can confidently identify the lenses and rule out the
non-lenses with our plausibility criteria.  Even though the plausibility
calculation involves fitting highly parametrized models of
astronomical sources and the varying point-spread function in many
pixels of imaging, it can be calculated in 
% seconds
a few minutes on contemporary
hardware; we comment on how this scales to ongoing lens searches in various wide
field imaging surveys.
\end{abstract}

@@

In this paper we ask the following questions:

\item Can a relative lens plausibility be reliably computed across a
realistic sample of pre-selected targets, such as those selected from the SDSS
spectroscopic object catalog during the SQLS?

\item What challenges will be faced when attempting a similar computation in a
wide-field imaging survey covering thousands of square degrees and potentially
millions of targets? And with which further approximations might these be
approached?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  SECTION 2: MODELS AND INFERENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Models and Inference}
\label{sec:model}

@@

% do these comment headers really help?
% after all, the \section{} commands say THE SAME THING
% PJM: Yes, they break up the text in the editor, making it easier to navigate
% through a long file.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We thank Sherry Suyu and James H.\ H.\ Chan, and Matt Auger and the STRIDES
collaboration for useful discussions and suggestions.
PJM acknowledges support from grants\ldots
DWH acknowledges support from grants\ldots
